\problemname{Blackjack}
Blackjack Bob, as his nickname suggests, likes to play Blackjack every chance he gets.
Bob has always played at the same casino, and every dealer knows he is unlike other players.
Bob's lucky number is $3$ and thus always asks for $3$ cards regardless of the risk of losing by asking for a third card before checking the previous $2$.

After his long career playing Blackjack, Bob has forgotten how to calculate the value of the hand dealt to him.
He still enjoys playing blackjack and has therefore asked his nephew to write down the values of the different cards.
Despite his nephew's horrible handwriting, Bob can determine the numerical cards' values of $2-10$ are the same as the number written on them.
He can also determine that the court cards \textit{Jack}, \textit{Queen} and \textit{King} have a value of $10$, while the \textit{Ace} can be either $1$ or $11$.
Despite his nephew's notes have helped him determine the cards' values, he still seems incapable of determining the best possible result of his dealt hand.
Can you help Bob determine the best possible hand from his given hand?
\section*{Input}

The first line of the input contains one integer $N$, $1 \leq N \leq 5$, which is the number of hands Blackjack Bob will be dealt.
The following $N$ lines contain three cards each representing a dealt hand to Bob.


\section*{Output}

For each hand output the best possible result.
Output "BLACKJACK" if the cards can add up to 21.
Output "LOST" if the sum of the card is more than 21.
Otherwise, output the largest sum possible.

